---
title: "MetropolitanAreas"
output: pdf_document
date: "2022-11-17"
---

# GDP and Income for Metropolitan Areas

The charts below show the relative wealth of metropolitan areas to the national average from 1969 to 2021. The data comes from the BEA (Bureau of Economic Analysis) and the data only goes as far back as 1969.

Notable trends:

1) Austin-Round Rock-Georgetown, TX actually used to be poorer than average until quite recently.

2) Detroit-Warren-Dearborn, MI had a large relative decline from 1969 to 2021. Actually, nearly all cities in Michigan are declining relative to the national average. The same applies for many nearby states, which is a reason why this area is often called the "Rust Belt".

3) Midland, TX became one of the richest cities due to the oil boom.

4) San Jose-Sunnyvale-Santa Clara, CA had a large relative increase from 2010 onwards, despite being one of the richer cities in the US already. San Jose/San Francisco are the only two cities in California that growing richer relative to the national average.

5) Seattle-Tacoma-Bellevue, WA had a large relative increase from 2010 onwards.

6) The Villages, FL is a famous retirement area that apparently used to be poor, but has caught up to the national average.


```{r setup, include=FALSE}
library(readxl)
Table <- read_excel("C:/Users/willi/Downloads/Table.xlsx",skip = 5)
library(ggplot2)
library(dplyr)
library(tidyr)
temp = stringr::str_split(Table[[2]], " \\(")
Table[[2]] = sapply(temp, function(x) x[1])
Relative = bind_rows(apply(Table[3:55], 1, function(x) x/Table[1,3:55]))
Relative = cbind(Table[2], Relative)
Relative = pivot_longer(Relative, cols = 2:54, names_to = "Year", values_to = "Relative")
Relative[[2]] = as.numeric(Relative[[2]])
Relative[[4]] = stringr::str_sub(Relative[[1]], start= -2)
```



```{r}
make_plot = function(x){
  minimum = min(0.8, min(x[[3]]))
  maximum = max(1.2, max(x[[3]]))
  name = paste0("Relative Personal Income per Capita (US = 1) 1969-2021 for \n", x[[1]][1])
  ggplot(x, aes(x = Year, y = Relative)) +
    geom_point() +
    geom_line() +
    theme_bw() + 
    ylim(minimum, maximum) +
    ggtitle(name)
}

make_plot_state = function(x){
  x[[1]] = stringr::str_sub(x[[1]], end = 10)
  minimum = min(0.8, min(x[[3]]))
  maximum = max(1.2, max(x[[3]]))
  name = paste0("Relative Personal Income per Capita (US = 1) 1969-2021 for cities in \n", x[[4]][1])
  ggplot(x, aes(x = Year, y = Relative, color = GeoName)) +
    geom_point() +
    geom_line() +
    theme_bw() + 
    ylim(minimum, maximum) +
    ggtitle(name)
}
make_plot_city = function(x){
  minimum = min(0.8, min(x[[3]]))
  maximum = max(1.2, max(x[[3]]))
  name = paste0("Relative Personal Income per Capita (US = 1) 1969-2021")
  ggplot(x, aes(x = Year, y = Relative, color = GeoName)) +
    geom_point() +
    geom_line() +
    theme_bw() + 
    ylim(minimum, maximum) +
    ggtitle(name) +
    theme(legend.title = element_text(size = 6), 
               legend.text = element_text(size = 6))
}
```

```{r}
Relative_Cities = group_split(Relative, GeoName)
Plots = lapply(Relative_Cities, make_plot)
```

```{r}
Plots
```


```{r}
Relative_States = group_split(Relative, ...4)
Relative_Plots = lapply(Relative_States, make_plot_state)
```

```{r}
Relative_Plots[1:50]
```


```{r}
Plot = make_plot_city(Relative %>%
  filter(GeoName %in% c("San Francisco-Oakland-Berkeley, CA", "San Jose-Sunnyvale-Santa Clara, CA",
                        "Los Angeles-Long Beach-Anaheim, CA", "Chicago-Naperville-Elgin, IL-IN-WI",
                        "Austin-Round Rock-Georgetown, TX", "New York-Newark-Jersey City, NY-NJ-PA",
                        "Miami-Fort Lauderdale-Pompano Beach, FL", "Boston-Cambridge-Newton, MA-NH",
                        "Houston-The Woodlands-Sugar Land, TX")))
Plot
```



```{r}
Plot = make_plot_city(Relative %>%
  filter(GeoName %in% c("San Francisco-Oakland-Berkeley, CA", "San Jose-Sunnyvale-Santa Clara, CA",
                        "Los Angeles-Long Beach-Anaheim, CA", "San Diego-Chula Vista-Carlsbad, CA",
                        "Riverside-San Bernardino-Ontario, CA", "Fresno, CA", "Sacramento-Roseville-Folsom, CA")))
Plot
```

# Wages

```{r}
Table <- read_excel("C:/Users/willi/Downloads/Table (1).xlsx",skip = 5)
temp = stringr::str_split(Table[[2]], " \\(")
Table[[2]] = sapply(temp, function(x) x[1])
Relative = bind_rows(apply(Table[3:55], 1, function(x) x/Table[1,3:55]))
Relative = cbind(Table[2], Relative)
Relative = pivot_longer(Relative, cols = 2:54, names_to = "Year", values_to = "Relative")
Relative[[2]] = as.numeric(Relative[[2]])
Relative[[4]] = stringr::str_sub(Relative[[1]], start= -2)
```



```{r}
make_plot = function(x){
  minimum = min(0.8, min(x[[3]]))
  maximum = max(1.2, max(x[[3]]))
  name = paste0("Relative Average Wages and Salaries (US = 1) 1969-2021 for \n", x[[1]][1])
  ggplot(x, aes(x = Year, y = Relative)) +
    geom_point() +
    geom_line() +
    theme_bw() + 
    ylim(minimum, maximum) +
    ggtitle(name)
}

make_plot_state = function(x){
  x[[1]] = stringr::str_sub(x[[1]], end = 10)
  minimum = min(0.8, min(x[[3]]))
  maximum = max(1.2, max(x[[3]]))
  name = paste0("Relative Average Wages and Salaries (US = 1)  1969-2021 for cities in \n", x[[4]][1])
  ggplot(x, aes(x = Year, y = Relative, color = GeoName)) +
    geom_point() +
    geom_line() +
    theme_bw() + 
    ylim(minimum, maximum) +
    ggtitle(name)
}
make_plot_city = function(x){
  minimum = min(0.8, min(x[[3]]))
  maximum = max(1.2, max(x[[3]]))
  name = paste0("Relative  Average Wages and Salaries (US = 1) 1969-2021")
  ggplot(x, aes(x = Year, y = Relative, color = GeoName)) +
    geom_point() +
    geom_line() +
    theme_bw() + 
    ylim(minimum, maximum) +
    ggtitle(name) +
    theme(legend.title = element_text(size = 6), 
               legend.text = element_text(size = 6))
}
```


```{r}
Relative_Cities = group_split(Relative, GeoName)
Plots = lapply(Relative_Cities, make_plot)
```

```{r}
Plots
```


```{r}
Relative_States = group_split(Relative, ...4)
Relative_Plots = lapply(Relative_States, make_plot_state)
```

```{r}
Relative_Plots[1:50]
```


```{r}
Plot = make_plot_city(Relative %>%
  filter(GeoName %in% c("San Francisco-Oakland-Berkeley, CA", "San Jose-Sunnyvale-Santa Clara, CA",
                        "Los Angeles-Long Beach-Anaheim, CA", "Chicago-Naperville-Elgin, IL-IN-WI",
                        "Austin-Round Rock-Georgetown, TX", "New York-Newark-Jersey City, NY-NJ-PA",
                        "Miami-Fort Lauderdale-Pompano Beach, FL", "Boston-Cambridge-Newton, MA-NH",
                        "Houston-The Woodlands-Sugar Land, TX")))
Plot
```



```{r}
Plot = make_plot_city(Relative %>%
  filter(GeoName %in% c("San Francisco-Oakland-Berkeley, CA", "San Jose-Sunnyvale-Santa Clara, CA",
                        "Los Angeles-Long Beach-Anaheim, CA", "San Diego-Chula Vista-Carlsbad, CA",
                        "Riverside-San Bernardino-Ontario, CA", "Fresno, CA", "Sacramento-Roseville-Folsom, CA")))
Plot
```