---
title: "BodyFat"
output: pdf_document
date: "2023-07-18"
---

# National Health and Nutrition Examination Survey 2017-2018

The NHANES includes DEXA scan of participants age 8-59, which allows researchers to calculate the body fat percentage of participants.

A large amount of other data is also collected. Sampling weights are used to collect the data, so a simple arithmetic mean will not work. Instead, weighted means and weighted quantiles must be used to calculate any means and quantiles (in this case, percentiles). In this case `Hmisc::wtd.quantile` calculates weighted quantiles.

Waist/Height Ratio is a commonly used way to calculate a person's health, since calcalating a person's body fat percentage is difficult and hard to do. Even a DEXA scan is not perfectly accurate. Waist/Height Ratio may be a better alternative to BMI in many cases.

A Waist/Height Ratio of under 0.5 is optimal, but the majority of the population is above that, confirming that there is indeed an obesity crisis. As expected, Waist/Height Ratio, BMI, and Body Fat Percentage are all highly correlated with each other.

Women and men store fat differently, so body fat percentage that is healthy is different. For women, body fat percentage should be under 33% and for men, body fat percentage should be under 21%. 

For the last section, I use a linear model to calculate the estimated body fat percentage by BMI.

```{r setup}
library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
res = read_xpt("C:/Users/willi/Downloads/DXX_J.xpt")
demo = read_xpt("C:/Users/willi/Downloads/DEMO_J.xpt")
body = read_xpt("C:/Users/willi/Downloads/BMX_J.xpt")

total = demo %>%
  left_join(body, by = "SEQN") %>%
  left_join(res, by = "SEQN")

bf = total %>%
  mutate(Race = recode(RIDRETH3,
                       `1` = "Mexican American",
                       `2` = "Other Hispanic",
                       `3` = "Non-Hispanic White",
                       `4` = "Non-Hispanic Black",
                       `6` = "Non-Hispanic Asian",
                       `7` = "Other Race")) %>%
  mutate(Edu = recode(DMDEDUC2,
                      `1` = 	"Less than 12th grade",
                      `2` = 	"Less than 12th grade",	
                      `3` =	"High school graduate/GED or equivalent",
                      `4` =	"Some college or AA degree",
                      `5` = "College graduate or above",
                      `6` = "Other",
                      `7` = "Other",
                      .default = "Other")) %>%
  mutate(Sex = recode(RIAGENDR,
                      `1` = "Male",
                      `2` = "Female")) %>%
  filter(!is.na(DXDTOPF)) %>%
  filter(RIDAGEYR >= 25 & RIDAGEYR <= 59) %>%
  group_by(RIDAGEYR, Sex) %>%
  summarize(BodyFat05 = Hmisc::wtd.quantile(DXDTOPF, WTMEC2YR, probs = 0.05, normwt = TRUE),
            BodyFat10 = Hmisc::wtd.quantile(DXDTOPF, WTMEC2YR, probs = 0.1, normwt = TRUE),
            BodyFat25 = Hmisc::wtd.quantile(DXDTOPF, WTMEC2YR, probs = 0.25, normwt = TRUE),
            BodyFat50 = Hmisc::wtd.quantile(DXDTOPF, WTMEC2YR, probs = 0.5, normwt = TRUE))

bf = bf %>%
  pivot_longer(cols = 3:6, names_prefix = "BodyFat", names_to = "Body Fat Percentile", values_to = "Percent")

ggplot(bf, aes(x = RIDAGEYR, y = Percent, color = Sex, linetype = `Body Fat Percentile`, group = interaction(`Body Fat Percentile`, Sex))) + 
  theme_bw() + xlab("Age") + ylab("Body Fat Percentage")+
  labs(fill="Percentile and Sex") + 
  ggtitle("Body Fat Percentile by Age and Sex") +
  stat_smooth(se = FALSE, span = 0.65, formula = y ~ x, method = "loess")
```


```{r}
ratio = total %>%
  mutate(Race = recode(RIDRETH3,
                       `1` = "Mexican American",
                       `2` = "Other Hispanic",
                       `3` = "Non-Hispanic White",
                       `4` = "Non-Hispanic Black",
                       `6` = "Non-Hispanic Asian",
                       `7` = "Other Race")) %>%
  mutate(Edu = recode(DMDEDUC2,
                      `1` = 	"Less than 12th grade",
                      `2` = 	"Less than 12th grade",	
                      `3` =	"High school graduate/GED or equivalent",
                      `4` =	"Some college or AA degree",
                      `5` = "College graduate or above",
                      `6` = "Other",
                      `7` = "Other",
                      .default = "Other")) %>%
  mutate(Sex = recode(RIAGENDR,
                      `1` = "Male",
                      `2` = "Female")) %>%
  mutate(Ratio = BMXWAIST/BMXHT) %>%
  filter(RIDAGEYR >= 25 & RIDAGEYR <= 59) %>%
  group_by(RIDAGEYR, Sex) %>%
  summarize(BodyFat05 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.05, normwt = TRUE),
            BodyFat10 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.1, normwt = TRUE),
            BodyFat25 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.25, normwt = TRUE),
            BodyFat50 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.5, normwt = TRUE))

ratio = ratio %>%
  pivot_longer(cols = 3:6, names_prefix = "BodyFat", names_to = "Waist/Height Percentile", values_to = "Percent")

ggplot(ratio, aes(x = RIDAGEYR, y = Percent, color = Sex, linetype = `Waist/Height Percentile`, group = interaction(`Waist/Height Percentile`, Sex))) + 
  theme_bw() + xlab("Age") + ylab("Waist/Height Ratio")+
  labs(fill="Percentile and Sex") + 
  ggtitle("Waist/Height Percentile by Age and Sex") +
  stat_smooth(se = FALSE, span = 0.65, formula = y ~ x, method = "loess")
```


```{r}
ratio = total %>%
  mutate(Race = recode(RIDRETH3,
                       `1` = "Mexican American",
                       `2` = "Other Hispanic",
                       `3` = "Non-Hispanic White",
                       `4` = "Non-Hispanic Black",
                       `6` = "Non-Hispanic Asian",
                       `7` = "Other Race")) %>%
  mutate(Edu = recode(DMDEDUC2,
                      `1` = 	"Less than 12th grade",
                      `2` = 	"Less than 12th grade",	
                      `3` =	"High school graduate/GED or equivalent",
                      `4` =	"Some college or AA degree",
                      `5` = "College graduate or above",
                      `6` = "Other",
                      `7` = "Other",
                      .default = "Other")) %>%
  mutate(Sex = recode(RIAGENDR,
                      `1` = "Male",
                      `2` = "Female")) %>%
  mutate(Ratio = BMXWAIST/BMXHIP) %>%
  filter(RIDAGEYR >= 25 & RIDAGEYR <= 59) %>%
  group_by(RIDAGEYR, Sex) %>%
  summarize(BodyFat05 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.05, normwt = TRUE),
            BodyFat10 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.1, normwt = TRUE),
            BodyFat25 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.25, normwt = TRUE),
            BodyFat50 = Hmisc::wtd.quantile(Ratio, WTMEC2YR, probs = 0.5, normwt = TRUE))

ratio = ratio %>%
  pivot_longer(cols = 3:6, names_prefix = "BodyFat", names_to = "Waist/Hip Percentile", values_to = "Percent")

ggplot(ratio, aes(x = RIDAGEYR, y = Percent, color = Sex, linetype = `Waist/Hip Percentile`, group = interaction(`Waist/Hip Percentile`, Sex))) + 
  theme_bw() + xlab("Age") + ylab("Waist/Hip Ratio")+
  labs(fill="Percentile and Sex") + 
  ggtitle("Waist/Hip Percentile by Age and Sex") +
  stat_smooth(se = FALSE, span = 0.65, formula = y ~ x, method = "loess")
```


```{r}
total = total %>%
  filter(RIDAGEYR >= 20 & RIDAGEYR <= 59)
gg = lm(DXDTOPF ~ BMXWAIST + I(BMXWAIST^2) + BMXHT + BMXHIP + RIAGENDR + factor(RIDRETH3), data = total)
total$BodyFatPredict = predict(gg, total)
```


```{r}
bf = total %>%
  mutate(Race = recode(RIDRETH3,
                       `1` = "Mexican American",
                       `2` = "Other Hispanic",
                       `3` = "Non-Hispanic White",
                       `4` = "Non-Hispanic Black",
                       `6` = "Non-Hispanic Asian",
                       `7` = "Other Race")) %>%
  mutate(Edu = recode(DMDEDUC2,
                      `1` = 	"Less than 12th grade",
                      `2` = 	"Less than 12th grade",	
                      `3` =	"High school graduate/GED or equivalent",
                      `4` =	"Some college or AA degree",
                      `5` = "College graduate or above",
                      `6` = "Other",
                      `7` = "Other",
                      .default = "Other")) %>%
  mutate(Sex = recode(RIAGENDR,
                      `1` = "Male",
                      `2` = "Female")) %>%
  filter(!is.na(BodyFatPredict)) %>%
  filter(RIDAGEYR >= 25 & RIDAGEYR <= 59) %>%
  group_by(RIDAGEYR, Sex) %>%
  summarize(BodyFat05 = Hmisc::wtd.quantile(BodyFatPredict, WTMEC2YR, probs = 0.05, normwt = TRUE),
            BodyFat10 = Hmisc::wtd.quantile(BodyFatPredict, WTMEC2YR, probs = 0.1, normwt = TRUE),
            BodyFat25 = Hmisc::wtd.quantile(BodyFatPredict, WTMEC2YR, probs = 0.25, normwt = TRUE),
            BodyFat50 = Hmisc::wtd.quantile(BodyFatPredict, WTMEC2YR, probs = 0.5, normwt = TRUE))


below15 = total %>%
  filter(RIAGENDR == 1 & !is.na(DXDTOPF)) %>%
  mutate(Below15 = ifelse(DXDTOPF <= 15, 1, 0)) %>%
  group_by(RIDAGEYR) %>%
  summarize(Below15 = weighted.mean(Below15, WTMEC2YR))

bf = bf %>%
  pivot_longer(cols = 3:6, names_prefix = "BodyFat", names_to = "Body Fat Percentile", values_to = "Percent")

ggplot(bf, aes(x = RIDAGEYR, y = Percent, color = Sex, linetype = `Body Fat Percentile`, group = interaction(`Body Fat Percentile`, Sex))) + 
  theme_bw() + xlab("Age") + ylab("Body Fat Percentage")+
  labs(fill="Percentile and Sex") + 
  ggtitle("Body Fat Percentile (Estimated with Formula) by Age and Sex") +
  stat_smooth(se = FALSE, span = 0.65, formula = y ~ x, method = "loess")
```


# BMI vs Body Fat Percentage from DEXA Scan

```{r}
total = total %>%
  filter(RIDAGEYR >= 20 & RIDAGEYR <= 50)
ggplot(total %>% filter(RIAGENDR == 1), aes(x = DXDTOPF, BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + ylim(15, 40) + xlim(10, 45) + theme_bw() + xlab("Body Fat Percentage") + ylab("BMI") + ggtitle("Body Fat Percentage and BMI for Males Age 20-50")
```


```{r}
ggplot(total %>% filter(RIAGENDR == 1 & BMXHT >= 173 & BMXHT <= 180), aes(x = DXDTOPF, BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + ylim(15, 40) + xlim(10, 45) + theme_bw() + xlab("Body Fat Percentage") + ylab("BMI") + ggtitle("Body Fat Percentage and BMI for Males Age 20-50 (Height 173-180 cm)")
```



```{r}
ggplot(total %>% filter(RIAGENDR == 2), aes(x = DXDTOPF, BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + ylim(15, 40) + xlim(15, 50) + theme_bw() + xlab("Body Fat Percentage") + ylab("BMI") + ggtitle("Body Fat Percentage and BMI for Females Age 20-50")
```


```{r}
ggplot(total %>% filter(RIAGENDR == 1), aes(y = DXDTOPF, x = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + xlim(15, 40) + ylim(10, 45) + theme_bw() + ylab("Body Fat Percentage") + xlab("BMI") + ggtitle("BMI and Body Fat Percentage for Males Age 20-50")
```


```{r}
ggplot(total %>% filter(RIAGENDR == 2), aes(y = DXDTOPF, x = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + xlim(15, 40) + ylim(15, 50) + theme_bw() + ylab("Body Fat Percentage") + xlab("BMI") + ggtitle("BMI and Body Fat Percentage for Females Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1), aes(x = BMXWAIST, y = DXDTOPF)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("Body Fat Percentage") + xlab("Waist Circumference (cm)") + ggtitle("Waist Circumference and Body Fat Percentage for Males Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1 & BMXHT >= 173 & BMXHT <= 180), aes(x = BMXWAIST, y = DXDTOPF)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("Body Fat Percentage") + xlab("Waist Circumference (cm)") + ggtitle("Waist Circumference and Body Fat Percentage for Males Age 20-50 (Height 173-180 cm)")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 2), aes(x = BMXWAIST, y = DXDTOPF)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("Body Fat Percentage") + xlab("Waist Circumference (cm)") + ggtitle("Waist Circumference and Body Fat Percentage for Females Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 2) %>% mutate(Ratio = BMXWAIST/BMXHIP), aes(x = Ratio, y = DXDTOPF)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("Body Fat Percentage") + xlab("Waist/Hip Ratio") + ggtitle("Waist/Hip Ratio and Body Fat Percentage for Females Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1) %>% mutate(Ratio = BMXWAIST/BMXHIP), aes(x = Ratio, y = DXDTOPF)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("Body Fat Percentage") + xlab("Waist/Hip Ratio") + ggtitle("Waist/Hip Ratio and Body Fat Percentage for Males Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 2) %>% mutate(Ratio = BMXWAIST/BMXHIP), aes(x = Ratio, y = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("BMI") + xlab("Waist/Hip Ratio") + ggtitle("Waist/Hip Ratio and BMI for Females Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1) %>% mutate(Ratio = BMXWAIST/BMXHIP), aes(x = Ratio, y = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("BMI") + xlab("Waist/Hip Ratio") + ggtitle("Waist/Hip Ratio and BMI for Males Age 20-50")
```



```{r}
ggplot(total %>% filter(RIAGENDR == 2) %>% mutate(Ratio = BMXWAIST/BMXHT), aes(x = Ratio, y = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("BMI") +  ylim(15, 60) + xlab("Waist/Height Ratio") + ggtitle("Waist/Height Ratio and BMI for Females Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1) %>% mutate(Ratio = BMXWAIST/BMXHT), aes(x = Ratio, y = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("BMI") + ylim(15, 60) + xlab("Waist/Height Ratio") + ggtitle("Waist/Height Ratio and BMI for Males Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1) %>% mutate(Ratio = BMXWAIST/BMXHT), aes(x = Ratio, y = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("BMI") + ylim(15, 60) + xlab("Waist/Height Ratio") + ggtitle("Waist/Height Ratio and BMI for Males Age 20-50")
```


```{r}
ggplot(total %>% filter(RIAGENDR == 1) %>% mutate(Ratio = BMXWAIST/BMXHT, FFMI = BMXBMI * (100 - DXDTOPF)/100), aes(x = FFMI, y = Ratio)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("Waist/Height Ratio") + xlab("Fat Free Mass Index") + ggtitle("Fat Free Mass Index and Waist/Height Ratio for Males Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1) %>% mutate(FFMI = BMXBMI * (100 - DXDTOPF)/100), aes(x = FFMI, y = DXDTOPF)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("Body Fat Percentage") + xlab("Fat Free Mass Index") + ggtitle(" Fat Free Mass Index and Body Fat Percentage for Males Age 20-50")
```

```{r}
ggplot(total %>% filter(RIAGENDR == 1) %>% mutate(FFMI = BMXBMI * (100 - DXDTOPF)/100), aes(x = FFMI, y = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + theme_bw() + ylab("BMI") + ylim(15, 60) + xlab("Fat Free Mass Index") + ggtitle(" Fat Free Mass Index and BMI for Males Age 20-50")
```


```{r}
get_bf = function(waist, height, hip, race = 6, gender){
  predict(gg, data.frame(BMXWAIST = waist * 2.54, BMXHT = height * 2.54, RIDRETH3 = race, BMXHIP = hip * 2.54, RIAGENDR = gender))
}
```


# BMI vs Body Fat Percentage Estimated


```{r}
total$DXDTOPF = total$BodyFatPredict
ggplot(total %>% filter(RIAGENDR == 1), aes(x = DXDTOPF, BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + ylim(15, 40) + xlim(10, 45) + theme_bw() + xlab("Estimated Body Fat Percentage") + ylab("BMI") + ggtitle("Estimated Body Fat Percentage and BMI for Males Age 20-50")
```


```{r}
ggplot(total %>% filter(RIAGENDR == 2), aes(x = DXDTOPF, BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + ylim(15, 40) + xlim(15, 50) + theme_bw() + xlab("Estimated Body Fat Percentage") + ylab("BMI") + ggtitle("Estimated Body Fat Percentage and BMI for Females Age 20-50")
```


```{r}
ggplot(total %>% filter(RIAGENDR == 1), aes(y = DXDTOPF, x = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + xlim(15, 40) + ylim(10, 45) + theme_bw() + ylab("Estimated Body Fat Percentage") + xlab("BMI") + ggtitle("BMI and Estimated Body Fat Percentage for Males Age 20-50")
```


```{r}
ggplot(total %>% filter(RIAGENDR == 2), aes(y = DXDTOPF, x = BMXBMI)) + geom_point() + stat_smooth(se = FALSE) + xlim(15, 40) + ylim(15, 50) + theme_bw() + ylab("Estimated Body Fat Percentage") + xlab("BMI") + ggtitle("BMI and Estimated Body Fat Percentage for Females Age 20-50")
```



