---
title: "Vehicles Registered"
output:
  pdf_document: default
  html_document: default
date: "2023-01-17"
---

# Vehicles Registered in California

The California DMV releases data on the number of registered vehicles by model year, make, and fuel type by Zip Code. This allows for calculating what percent of vehicles registered are electric vehicles or by brand for every model year.

Clearly, the number of electric vehicles is growing in California. Most of these electric vehicles are from Tesla. The data can be found here: https://data.ca.gov/dataset/vehicle-fuel-type-count-by-zip-code



```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
vehicles = read.csv("C:/Users/willi/Downloads/vehicle-fuel-type-count-by-zip-code-2022.csv")

tab = vehicles %>%
  group_by(Zip.Code, Model.Year) %>%
  mutate(percent =  100 * Vehicles/sum(Vehicles)) %>% 
  ungroup %>%
  group_by(Zip.Code, Model.Year, Make) %>%
  summarize(Vehicles = sum(Vehicles), Percent = sum(percent)) 



```


```{r}
zi = tab %>%
  filter(Model.Year != "<2009" &  Model.Year != "2023") %>% ungroup() %>% select(-Zip.Code)
other_zi = zi %>%
  mutate(Make = recode(Make, "LEXUS" = "TOYOTA", "SCION" = "TOYOTA", "ACURA" = "HONDA", "INFINITI" = "NISSAN",
                       "KIA" = "HYUNDAI", "AUDI" = "VOLKSWAGEN", "PORSCHE" = "VOLKSWAGEN")) %>%
  group_by(Model.Year, Make) %>%
  summarize(Vehicles = sum(Vehicles), Percent = sum(Percent))
comb = other_zi %>%
  filter(!(Make %in% c("TOYOTA", "HONDA", "TESLA", "NISSAN", "SUBARU", "HYUNDAI", "FORD", "VOLKSWAGEN"))) %>%
  group_by(Model.Year) %>%
  summarize(Make = "OTHER", Vehicles = sum(Vehicles), Percent = sum(Percent))
comb = rbind(other_zi, comb) 
result = comb %>%
  filter(Make %in% c("TOYOTA", "HONDA", "TESLA", "NISSAN", "LEXUS", "SUBARU", "HYUNDAI", "FORD", "VOLKSWAGEN", "OTHER")) %>%
  mutate(Make = recode(Make, "TOYOTA" = "Toyota+Lexus", "HONDA" = "Honda+Acura", "NISSAN" = "Nissan+Infiniti",
                       "VOLKSWAGEN" = "Volkswagen Group", "HYUNDAI" = "Hyundai+Kia",
                       "LEXUS" = "Lexus", "SUBARU" = "Subaru", "FORD" = "Ford", "OTHER" = "Other Brands", "TESLA" = "Tesla")) %>%
  ggplot(aes(x = Model.Year, y = Vehicles, group = Make, color = Make)) +
    geom_point() + geom_line() + theme_bw() + 
    xlab("Model Year") +
    guides(x = guide_axis(angle = 45)) +
    ylab("Number of Registered Vehicles") +
    ggtitle("Number of Registered Vehicles by Brand and Model Year for California")
```



```{r}
tab2 = vehicles %>%
  group_by(Model.Year) %>%
  mutate(percent =  100 * Vehicles/sum(Vehicles)) %>% 
  ungroup %>%
  group_by(Model.Year, Make) %>%
  summarize(Vehicles = sum(Vehicles), Percent = sum(percent)) %>%
  filter(Model.Year != "<2009" & Model.Year != "2023")
other_zi = tab2 %>%
  mutate(Make = recode(Make, "LEXUS" = "TOYOTA", "SCION" = "TOYOTA", "ACURA" = "HONDA", "INFINITI" = "NISSAN",
                       "KIA" = "HYUNDAI", "AUDI" = "VOLKSWAGEN", "PORSCHE" = "VOLKSWAGEN")) %>%
  group_by(Model.Year, Make) %>%
  summarize(Vehicles = sum(Vehicles), Percent = sum(Percent))
comb = other_zi %>%
  filter(!(Make %in% c("TOYOTA", "HONDA", "TESLA", "NISSAN", "SUBARU", "HYUNDAI", "FORD", "VOLKSWAGEN"))) %>%
  group_by(Model.Year) %>%
  summarize(Make = "OTHER", Vehicles = sum(Vehicles), Percent = sum(Percent))
comb = rbind(other_zi, comb) 
result2 = comb %>%
  filter(Make %in% c("TOYOTA", "HONDA", "TESLA", "NISSAN", "LEXUS", "SUBARU", "HYUNDAI", "FORD", "VOLKSWAGEN", "OTHER")) %>%
  mutate(Make = recode(Make, "TOYOTA" = "Toyota+Lexus", "HONDA" = "Honda+Acura", "NISSAN" = "Nissan+Infiniti",
                       "VOLKSWAGEN" = "Volkswagen Group", "HYUNDAI" = "Hyundai+Kia",
                       "LEXUS" = "Lexus", "SUBARU" = "Subaru", "FORD" = "Ford", "OTHER" = "Other Brands", "TESLA" = "Tesla")) %>%
  ggplot(aes(x = Model.Year, y = Percent, group = Make, color = Make)) +
    geom_point() + geom_line() + theme_bw() + 
    xlab("Model Year") + 
    guides(x = guide_axis(angle = 45)) +
    ylab("Percent of Registered Vehicles") +
    ggtitle("Percent of Registered Vehicles by Brand and Model Year for California")
```




```{r}
tab2 = vehicles %>%
  group_by(Model.Year) %>%
  mutate(percent =  100 * Vehicles/sum(Vehicles)) %>% 
  ungroup %>%
  group_by(Model.Year, Fuel) %>%
  summarize(Vehicles = sum(Vehicles), Percent = sum(percent)) %>%
  filter(Model.Year != "<2009" & Model.Year != "2023") %>%
  ggplot(aes(x = Model.Year, y = Percent, color = Fuel, group = Fuel)) +
    geom_point() + geom_line() + theme_bw() + 
    xlab("Model Year") + 
    guides(x = guide_axis(angle = 45)) +
    ylab("Percent of Registered Vehicles") +
    ggtitle("Percent of Vehicles by Fuel Type for California")
```


```{r}
result
result2
tab2
```

